HEP Software Foundation Community White Paper Working Group -- Data Processing Frameworks

### 2018-10-19 CWP/papers/HSF-CWP-2017-08_framework/latex/df_fwk_summary.tex
Improve references
Found what references I could and removed all of the
placeholders

\author{HEP Software Foundation:}
\author[d]{Paolo Calafiura}
\author[a,1]{Benadikt Hegner}
\author[c]{Chris Jones}
\author[b]{Michel Jouvin}
\author[c,1]{Jim Kowalkowski}
\author[c,1]{Elizabeth Sexton-Kennedy}
\author[a]{Graeme A Stewart}
\author[d]{Several Others - Charles, Marco, ?}

\affiliation[a]{CERN, Geneva, Switzerland}
\affiliation[b]{LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\affiliation[c]{Fermi National Accelerator Laboratory, Batavia, Illinois, USA}
\affiliation[d]{Lawrence Berkeley National Laboratory, Berkeley, CA, USA}
\affiliation[e]{Other Places}
\affiliation[1]{Paper Editor}

@@

Although most frameworks used in HEP share common concepts, there are,
for mainly historical reasons, a number of different implementations;
some of these are shared between experiments. A complete description
of framework use cases written for the Gaudi collaboration is
described in {[}2.fixme{]} and these are sufficiently general to apply
to all HEP experiments. The Gaudi framework {[}70{]} was originally
developed by LHCb, but is also used by ATLAS and various non-LHC
experiments. CMS uses its own CMSSW framework~\cite{Bayatian:2006nff},
{[}71{]} which was forked to provide the art framework for the Fermilab
Intensity Frontier experiments~\cite{Green:2012gv},{[}72{]}.  Belle II uses
basf2~\cite{1742-6596-331-3-032024},{[}73{]}. The linear collider community
developed and uses Marlin~\cite{Gaede:2006pj},{[}74{]}. The FAIR experiments
use FairROOT, closely related to ALICE's AliROOT. The FAIR experiments
and ALICE are now developing a new framework, which is called
O2~\cite{O2},{[}75{]}. At the time of writing, most major frameworks support
basic parallelisation, both within and across events, based on a
task-based model~\cite{Jones:2015soc,Clemencic:2015paa}. O2 already
includes additional multi-node setups and communication.

>>>>

\author{HEP Software Foundation:}
\author[d]{Paolo Calafiura}
\author[a,1]{Benadikt Hegner}
\author[c]{Chris Jones}
\author[b]{Michel Jouvin}
\author[c,1]{Jim Kowalkowski}
\author[c,1]{Elizabeth Sexton-Kennedy}
\author[a]{Graeme A Stewart}
%\author[e]{Several Others - Charles, Marco, ?}

\affiliation[a]{CERN, Geneva, Switzerland}
\affiliation[b]{LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\affiliation[c]{Fermi National Accelerator Laboratory, Batavia, Illinois, USA}
\affiliation[d]{Lawrence Berkeley National Laboratory, Berkeley, CA, USA}
%\affiliation[e]{Other Places}
\affiliation[1]{Paper Editor}

@@

Although most frameworks used in HEP share common concepts, there are,
for mainly historical reasons, a number of different implementations;
some of these are shared between experiments. A complete description
of framework use cases written for the Gaudi collaboration is
described in \cite{Maley:684466} and these are sufficiently general to apply
to all HEP experiments. The Gaudi framework \cite{Barrand:2001ny,1742-6596-219-4-042006} was originally
developed by LHCb, but is also used by ATLAS and various non-LHC
experiments. CMS uses its own CMSSW framework~\cite{Bayatian:2006nff}
which was forked to provide the art framework for the Fermilab
Intensity Frontier experiments~\cite{Green:2012gv}.  Belle II uses
basf2~\cite{1742-6596-331-3-032024}. The linear collider community
developed and uses Marlin~\cite{Gaede:2006pj}. The FAIR experiments
use FairROOT, closely related to ALICE's AliROOT. The FAIR experiments
and ALICE are now developing a new framework, which is called
O2~\cite{O2,1742-6596-664-8-082046}. At the time of writing, most major frameworks support
basic parallelisation, both within and across events, based on a
task-based model~\cite{Jones:2015soc,Clemencic:2015paa}. O2 already
includes additional multi-node setups and communication.
